---
title: "Alcohol vs Seat choice"
author: "Michael Recinos"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

 From what the graph shows we are able to see that the box for students sitting in the back if the class is much bigger then those who seat in the front and middle, leading to the understanding the students who sit in the back are more likely to pick up alcohol.
 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

this graphs shows the amount of drinks students in different parts of a class drink per week, showing that the students in the back of the class drink much more then both the students in the front and middle of the class. with students in the front drinking  1.78... drinks, the students in the middle drinking only 3.33... drink and the students in the back taking the largest number drinking 8.55... drinks pre week.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
this graph shows a significant result, because the number are much smaller then 0.05.

```{r}
plot(TukeyHSD(model1))
```
this graph shows the amount of differences each sits drink. letting the viewer realized that both the student in the front of the class and the students in the middle of the class are drink about the same as each other not one of them over does it, however the students in the back of the class completely take over the amount drink-ed by both front and middle seats.

## Conclusions

In conclusion the students who sit at the back of the class are more likely to drink. this is shown in all three graph, in which students in front and middle seats drink a low and similar amount the students in the back seat go on to drink much more. 
